A saturation model for impaired learning with enhanced plasticity: Supplementary material

### 2014-02-10 MHCpaper/MHCsupp.tex
Intuitive explanation of binary model failure

>>>>

Because for this simple binary synapse model, the ratio of the numbers of potentiated and depressed synapses is equal to the ratio of the potentiating and depressing transition rates. 
This means that the leading effects of enhanced intrinsic plasticity rates and saturation bias cancel each other. 
This is eve true as the number of synapses available for further plasticity approaches zero, which requires that the depressing transition be infinitely stronger than the potentiating transition, compensating for the saturation. 
There is a requirement that the total number of synapses, potentiated and depressed, is fixed. 
This normalization effect always dampens the effect of saturation bias, so that the effect of enhanced intrinsic plasticity rates always dominates. 
Thus, we always see enhanced learning with enhanced plasticity with the binary synapse model.
